Can machine learning correct microwave humidity radiances for the influence of clouds?

### 2021-02-11 Article/Review_1/response_reviewer_1.tex

\textbf{	Interactive comment on ``Can machine learning
	correct microwave humidity radiances for the
	influence of clouds?'' by Inderpreet Kaur et al.}

\begin{itemize}

\item 	precipitation and most dense clouds" I think the hydrometeor size is an important

\textcolor{blue}{Reply: We agree that the hydrometeor size is an important aspect, but when it comes to an overview of the cloud contamination at 183\,GHz, precipitating clouds and clouds with large optical thickness have the strongest effect, and a dense cloud could be composed of hydrometeors of different shapes and size. }

@@

\item	L66: ``only using measurements (no background data involved)'' My understanding is
		that the method is in theory model-free, but for the demonstration in this study, sim-
		ulations (e.g. background simulated at MWHS2 frequency) are used. Am I correct?
		Maybe this should be stressed here. Why not try with real MWHS2 observation for the
		all sky dataset?

\textcolor{blue}{Reply: Yes, the demonstration of the entire concept is based on simulations. We do not try with the real MWHS-2 observations as the validation of the training process could only be performed against clear-sy simulations. To stress on the fact that only background MWHS-2 observations are used, we have added the following text to Sect. 2.1.1:
``\textit{For the demonstation of the study, MWHS-2 background observations or simulations are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.2.1.1}''}

\item
		L137 "Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, Gaussian noise is added according to the chan-
		nel NEDT (Table 1 - Table 3)." Are the errors arising from the radiative transfer calculation accounted for?

@@

\end{itemize}

		\textbf{Questions:}
		\newline
\begin{itemize}

\item	
		Is this method applicable to IR e.g. to an ATOVS system?

\textcolor{blue}{Reply:  Yes, the method could potentially be applied to IR. The operation and  performance of the cloud correction approach is based on the fact that different frequencies have varying sensitivity to cloud signatures in the same field of view. For IR, infact, this feature is regularly used to flag out cloud contamination. Most cloud flagging schemes for IR are based on brightness temperature thresholds.
}

@@

\item	Could the uncertainty use for weak constraint 4dvar?

\textcolor{blue}{Reply:}

\item	
		What is the resource cost of this method (is this fast enough to be used in 1-h regional
		nwp with 30min window)?

\textcolor{blue}{Reply:  Yes, it would be feasible to implement the scheme into existing NWP models. In this study, QRNN was not optimized to get the maximum computational performance. However, with the modern computing architectures a much faster computation can be expected. }

### 2021-02-11 Article/Review_1/response_reviewer_2.tex

\textbf{
	Interactive comment on ``Can machine learning
	correct microwave humidity radiances for the
	influence of clouds?'' by Inderpreet Kaur et al.}

\begin{itemize}

\item 			
			As I understand it, this study uses only simulated measurements (either with or without hydrometeors included), even for MWHS-2 for which actual measurements are available. This should be made clearer, especially given line 66, which states that no``background'' data is required for the method. I'd also like to see a bit more discussion 	about whether the results you present should be expected to hold for real data. An assumption that you are making is that your forward model can represent real clouds with enough fidelity that a model trained on simulated data will still work on real-world data. Can you point to any evidence to back up this assumption? Have you tried comparing the histograms of model-simulated Tbs with real-world MWHS-2 Tbs?

\textcolor{blue}{Reply: We agree with the reviewer, the line 66, can be confusing. We have rearranged the text to give clarity.
Regarding the the discussion about simulations holding well for the real-data, we have added a new subsection () under Discussion.
Also, MWHS-2 simulations used in the study are the background radiance simulated by ECMWF for their assimilation systems. Their observational error model is already described in literature e.g. Lawrence et al., 2015. }

@@

\item  	
			What is the computational cost of the QRNN method compared to simpler cloud-
			clearing filters? Could it feasibly be implemented into existing NWP models given
			current computational constraints?

\textcolor{blue}{Reply: \textcolor{red}{add time} Yes, it would be feasible to implement the scheme into existing NWP models. It should be noted QRNN was not optimized to get the maximum computational performance. However, with the modern computing architectures a much faster computation can be expected. }

@@

\item  
			Lines 135-143: Why the large difference in number of cases simulated for ICI (220,000)
			vs. AWS (143,000), if they are both coming from the same population of CloudSat
			profiles? For the training dataset, you use about 75\% of total cases for MWHS-2,
			about 80\% of cases for ICI, and about 84\% of cases for AWS. Why this difference in
			proportions?

\textcolor{blue}{Reply: Yes, both ICI and AWS simulations come from same population of Cloudsat. For SMS, we had access to a smaller database, which was used for a earlier study. Due to difference in sizes of the available observations, maximum possible observations were incorporated to allow  representation to each cloud event. Even with differences in the database sizes, the results show that the predicted quantiles are well calibrated for all three sensors. With a larger database, one could expect similar or even better performance.}

@@

\item  
			Line 340: ``With a test dataset of 70 000 samples, we cannot represent the far wings of the distribution accurately.'' Couldn't one apply this same reasoning to Figures 2,3, or
			8, which have density values below $10^{-4}$ included?

\textcolor{blue}{Reply: Yes one could apply the same reasoning to the Figures 2, 3, or 8, but we prefer to show the complete distribution to emphasize that the cases with large errors occur infrequently. \textcolor{red}{Shall we show the complete dist?}}

\item 
			Figure 13: I wonder if there might be an easier, more concise way to evaluate whether
			the uncertainty intervals are properly calibrated. Namely, could you simply calculate
			how often the true value falls within the $\pm2\sigma$ uncertainty range, for each of the uncertainty bins ($0 - 3$K, $3 - 8$K, $8 +$ K) that you've included on the plot? If this percentage is significantly less than 95\%, it would suggests that your uncertainties are too small, while if it were closer to 100\% it would suggest your uncertainties are too large. Even if you don't get rid of Fig. 13, I think this would be useful information to include in the paper.

\textcolor{blue}{Reply: As per suggestion of the reviewer, we have included the information highlighting how well calibrated the uncertainties are. We add this information in Fig. 13. We provide the occurence percentage of true value for each uncertainty bin. We would also like to point out that Fig.6 and Fig.10 already show the calibration of uncertainty intervals, but this additional information reinforces the results further.}

### 2021-02-11 Article/ici_submm_cloudcorr_v1.1.tex
working on replies

In this study, we approach the cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. We denote this approach as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature also removes the need for defining threshold values, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear-sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach permits the full weight of
clear-sky data to be preserved.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.

For this study, MWHS-2 simulations were sourced from the operational ECMWF assimilation system.

@@

\subsection{Simulations}
%
MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF. In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively. These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects. Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$. With this filter, we have approximately 290\,000 cases.

@@

\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all SMS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

@@

To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy. Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship. Similar results are also obtained with SMS (not shown).

@@

>>>>

In this study, we approach the cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). Not only a best estimate is provided, but also a case-specific uncertainty. This information could be used as a pure filter, by rejecting data where the correction exceeds some threshold value. However, even better is to replace the original value with the predicted NFCS value when forming the clear-sky dataset. We denote this approach as cloud correction. This is done for each channel separately and by only using the measurements, although the scheme is demonstrated in the study by using simulated observations. It is shown below that a basically bias free cloud correction can be obtained. This feature also removes the need for defining threshold values, as long as the retrieval or assimilation system can incorporate the uncertainty of the corrected value. As also will be shown, the uncertainty for originally clear-sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach permits the full weight of
clear-sky data to be preserved.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89--191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered around 183\,GHz, and eight temperature sounding channels are centered on the 118\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}.

For the demonstation of the study, MWHS-2 background observations or simulations are used. Actual measurements are not taken into account. The requisite data was obtained from ECMWF. More details are described in Sect.~\ref{simulations}.

@@

\subsection{Simulations}
%
\label{simulations}
MWHS-2 simulated radiances during the period June--July 2020 are sourced from ECMWF. In the current version of the ECMWF Integrated Forecasting System (IFS), cycle 47R1 \citep{IFS47R1chap1}, clear-sky and all-sky radiative transfer are performed simultaneously for monitoring purposes, despite all humidity sounders being assimilated via all-sky exclusively. These side by side radiative transfer calculations on a large variety of model scenes provides an ideal dataset for comparing radiances with and without cloud effects. Out of all the available observations during the period, we use data for the latitudinal range: $60^{\degree}$\,S to $60^{\degree}$\,N and satellite zenith angle, less than $7.5^{\degree}$. With this filter, we have approximately 290\,000 cases.

@@

\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/fig12.pdf}	
	\caption{The average confidence intervals ($\pm3\sigma$) plotted against the magnitude of cloud impact for all SMS channels.}
	\label{fig:uncertainty_cloud_impact}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/fig13.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. The occurrence of true value in each uncertainty interval bin is given in the parentheses. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}
%f

@@

To conclude the results, we analyse if the uncertainty estimates given by QRNN are representative of prediction accuracy. Figure~\ref{fig:error_distribution_uncertainty_bins} shows the observed ICI errors binned by their corresponding uncertainty in $\pm\,2\sigma$  confidence interval. For all three channels, the spread of error distribution increases as the uncertainty about the accuracy of the prediction increases. The cases with high certainty have a narrow and sharp distribution, and the errors are mostly less than $\pm\,$2.5\,K. With increase in the uncertainty, frequency of cases with high accuracy decreases and the distributions spread out symmetrically to higher errors. Poor predictions occur more frequently when uncertainty is high. Cases with accurate predictions yet high uncertainty are also present. In spite of individual variations in the error distributions for each channel, predictions and their corresponding uncertainties follow the same relationship. We also evaluated if the uncertainty intervals are properly calibrated  Similar results are also obtained with SMS (not shown).

@@

\subsection{Cloud impact in simulations}

\todo{As mentioned in Sect.~{}, the MWHS-2 simulations are the background radiances simulated by ECMWF for their assimilation systems. The 
For ICI and SMS, the incorporate cloud variability by randomly selecting between three habits. But with only one particle size distribution (PSD), the true hydrometeor variability will be underestimated. But the all-sky DA systems, still assume a single PSD and habit combination. This can cause some model uncertainty and the mapping of cloud information from sub-mm channels to 183\,GHz shall not be perfect. Nonetheless, the advantge of the our scheme is that it allows to incorporate multiple PSD and habit variations and adapt to the local conditions.}
